\myTitle

### 2014-08-21 tex/main-body-text.tex
Add Kristen to acknowledments
caught one thing on final read through

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs with $K = 2$ to 4, {\sc flock} obtained a nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from {\sc structure}'s results
(Fig.~\ref{fig:qplots}). Of the `best runs' for the six groups for $K$ = 2, two  
runs yielded identical clustering (same mean LLOD score) while all other runs 
differed by at most the allocation of 13 individuals. As 
$K$ increased so did the number of solutions
that {\sc flock} found (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed---all intial 
allocations resulted in solutions that differed. 
{\sc flock} still produced estimates of the LLOD by individual for the 
'best run', however, it is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, surprisingly similar to
the partitions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

Despite the similar allocation of individuals into $K$ clusters, the 
plateau analysis to estimate $K$ in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from {\sc structure}. While no plateaus were observed in any of the six groups 
for a $K\geq 2$, the plateau record varied greatly among each
group for $K = 2$ (plateau sequences: Run1 = 3,2,3,7,4; Run2 = 2,5,2,3,2,3; Run3 = 2,2,2,2,2,5; 
Run4 = 2,3,4,2,4,3; Run5 = 2,2,5,5,3; and; Run6 = 2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to
either an estimate of K $\geq$ 2 (Run1) or {\em undecided} as a consequence of no plateau 
lengths being greater than 6. The ($\ln P(D)$) from {\sc structure}
was largest at $K$ = 6 which was further supported by the $q_i$ plots, however,
the $\Delta K$ method supported a $K$ of 3.

@@

\section*{Acknowledgments}
We are grateful to Robin Waples for helpful comments on a draft of this paper.

>>>>

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs with $K = 2$ to 4, {\sc flock} obtained a nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from {\sc structure}'s results
(Fig.~\ref{fig:qplots}). Of the `best runs' for the six groups for $K$ = 2, two  
runs yielded identical clustering (same mean LLOD score) while all other runs 
differed by at most the allocation of 13 individuals. As 
$K$ increased so did the number of solutions
that {\sc flock} found (Fig 1). For all groups of runs for $K > 2$, no plateaus were observed---all intial 
allocations resulted in solutions that differed. 
{\sc flock} still produced estimates of the LLOD by individual for the 
'best run', however, it is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, surprisingly similar to
the partitions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

Despite the similar allocation of individuals into $K$ clusters, the 
plateau analysis to estimate $K$ in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from {\sc structure}. While no plateaus were observed in any of the six groups 
for a $K > 2$, the plateau record varied greatly among each
group for $K = 2$ (plateau sequences: Run1 = 3,2,3,7,4; Run2 = 2,5,2,3,2,3; Run3 = 2,2,2,2,2,5; 
Run4 = 2,3,4,2,4,3; Run5 = 2,2,5,5,3; and; Run6 = 2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to
either an estimate of K $\geq$ 2 (Run1) or {\em undecided} as a consequence of no plateau 
lengths being greater than 6. The ($\ln P(D)$) from {\sc structure}
was largest at $K$ = 6 which was further supported by the $q_i$ plots, however,
the $\Delta K$ method supported a $K$ of 3.

@@

\section*{Acknowledgments}
We are grateful to Kristen Ruegg and Robin Waples for helpful comments on a draft of this paper.
